Graph-Based Neural Reconstruction \\ from Skeletonized 3D Networks

### 2017-11-15 papers/cvpr2018/0_introduction.tex
new title; edits to abstract and intro

\begin{figure}[t]
	\subfloat[]{
	\includegraphics[width=.47\linewidth]{figures/schema/pre-multicut-with-arrows.pdf}
	}	
	\subfloat[]{
	\includegraphics[width=.47\linewidth]{figures/schema/post-multicut.png}	
	}
	\caption{Example improvement of neural reconstruction. (a) We extract 3D skeletons from pixel-based segmentation algorithms to create a graph representation with error probabilities indicated by the red arrows. (b) We then improve the accuracy of segmentation labels using graph partitioning algorithms with local and global geometric features.}
	\label{fig:teaser}
\end{figure}

%\donglai{usually, top-down means split.. but we are also bottom-up, but with different representation}
The field of connectomics is concerned with reconstructing the wiring diagram of the brain at nanometer resolutions to enable new insights into the workings of the brain~\cite{haehn2017scalable,kasthuri2015saturated}. Recent advancements in image acquisition using multi-beam serial-section electron microscopy (sSEM) have allowed researchers to produce terabytes of image data every hour~\cite{hildebrand2017whole}. It is not feasible for domain experts to manually reconstruct thousands or millions of neurons from this vast amount of image data~\cite{haehn2014design}. State-of-the-art automatic reconstruction approaches use pixel-based segmentation with convolutional neural networks (CNNs) followed by agglomeration strategies~\cite{seymour2016rhoananet,lee2015recursive,nunez2014graph,parag2017anisotropic,ronneberger2015u,zlateski2015image}. %TODO DOUBLE CHECK REFERENCES
These \textit{bottom-up pixel-based} algorithms produce excellent results but still fall short of acceptable error rates for large volumes.

@@

We present a \textit{top-down graph-based} method that builds on the outputs of bottom-up pixel-based segmentation approaches. We first extract 3D skeletons from the input segmentation (Fig.~\ref{fig:pipeline}) and generate a simplified 3D graph (Fig.~\ref{fig:teaser}a). We train a 3D CNN classifier on the agglomerated regions in the segmentation data to detect errors. During test time, we run the classifier to populate the graph edge weights with error probabilities. We then use a graph optimization algorithm to partition the graph into the final reconstruction by enforcing domain-specific global constraints from the underlying biology (Fig.~\ref{fig:teaser}b).

Our approach operates at a level of abstraction above existing pixel-based methods. This allows us to leverage both local and global information to produce more accurate reconstructions. Since it uses agglomerated regions, our classifier is independent of image resolution and acquisition parameters, enabling its application to isotropic and anisotropic image data without retraining. Using the 3D graph of the segmentation allows us to enforce global constraints on the reconstruction that closely follow the underlying biology. We can also use local information such as shape priors to weight the edges in our graph. This dual approach of assessing local decisions in a global context yields accuracy improvements over the existing reconstruction methods.

This work makes the following following contributions: (1) a novel top-down graph-based method for neural reconstruction of connectomics data; (2) a region-based CNN classifier to detect errors under global constraints; (3) an empirical evaluation of our method on several connectomics datasets; (4) our method yields improved performance over the state-of-the-art on three testing datasets. On average, we improve the Variation of Information (VI) metric across all datasets by \FIX{X} percent without drastically increasing the running time.

>>>>

\begin{figure}[t]
	\subfloat[]{
	\includegraphics[width=.47\linewidth]{figures/schema/pre-multicut-with-arrows.pdf}
	}
	\subfloat[]{
	\includegraphics[width=.47\linewidth]{figures/schema/post-multicut.png}
	}
	\caption{Example improvement of neural reconstruction. (a) We extract 3D skeletons from pixel-based segmentation algorithms to create a 3D graph representation. Edges with high segmentation error probabilities are indicated by the red arrows. (b) We improve the accuracy of segmentation  using a graph partitioning algorithm, leveraging both local and global information.}
	\label{fig:teaser}
\end{figure}

%\donglai{usually, top-down means split.. but we are also bottom-up, but with different representation}
The field of connectomics is concerned with reconstructing the wiring diagram of the brain at nanometer resolutions to enable new insights into the workings of the brain~\cite{haehn2017scalable,kasthuri2015saturated}. Recent advancements in image acquisition using multi-beam serial-section electron microscopy (sSEM) have allowed researchers to produce terabytes of image data every hour~\cite{hildebrand2017whole}. It is not feasible for domain experts to manually reconstruct this vast amount of image data~\cite{haehn2014design}. State-of-the-art automatic reconstruction approaches use pixel-based segmentation with convolutional neural networks (CNNs) followed by agglomeration strategies~\cite{seymour2016rhoananet,lee2015recursive,nunez2014graph,parag2017anisotropic,ronneberger2015u,zlateski2015image}.
These \textit{bottom-up pixel-based} methods produce excellent results but still fall short of acceptable error rates for large volumes.

@@

We present a \textit{top-down graph-based} method that builds on the outputs of bottom-up pixel-based segmentation approaches. We first extract 3D skeleton networks from the input segmentation (Fig.~\ref{fig:pipeline}) and generate a simplified 3D graph (Fig.~\ref{fig:teaser}a). We train a CNN classifier on the agglomerated regions in the segmentation data to detect errors. We run the classifier to populate the graph edge weights with error probabilities. We then use a graph optimization algorithm to partition the graph into the final improved reconstruction by enforcing domain-specific global constraints from biology (Fig.~\ref{fig:teaser}b).

Our approach operates at a level of abstraction above existing pixel-based methods. This allows us to leverage both local and global information to produce more accurate reconstructions. Our method is independent of image resolution and acquisition parameters, enabling its application to isotropic and anisotropic image data without retraining. Using the 3D graph induced by the segmentation allows us to enforce global biological constraints on the reconstruction. Our dual approach of assessing local decisions in a global context yields accuracy improvements over existing reconstruction methods.

This work makes the following contributions: (1) a novel top-down method using  graphs from skeletonized 3D networks for improved neural reconstruction of connectomics data; (2) a region-based CNN classifier to detect errors using the 3D graph as global constraint; (3) an empirical evaluation of our method on several connectomics datasets; (4) our method yields improved performance over a state-of-the-art pixel-based reconstruction approach on average by \FIX{X} percent without drastically increasing the running time.

### 2017-11-15 papers/cvpr2018/paper.tex
new title; edits to abstract and intro

%%%%%%%%% TITLE
\title{Graph-Based Neural Reconstruction from Morphological Skeletons}

%Robust Agglomeration using 3D Skeletonization of Labeled for Connectomics}

@@

%%%%%%%%% ABSTRACT
\begin{abstract}
Advancements in electron microscopy image acquisition have created massive connectomics datasets in the terabyte range that make manual reconstruction of neuronal structures infeasible. 
Current state-of-the-art automatic methods segment neural membranes at the pixel level followed by agglomeration methods to create full neuron reconstructions. 
However, these approaches widely neglect global geometric properties that are inherent in the graph structure of neural wiring diagrams.
In this work, we follow bottom-up pixel-based reconstruction by a top-down graph-based method to more accurately approximate neural pathways. 
Using the membrane labels of the pixel-based segmentation we first generate skeletons in 3D.
Using this 3D graph we train automatic classifiers for shape description to detect impossible neural pathways by looking at geometric properties.
We then apply efficient graph-based optimization strategies to improve the segmentation labels. We demonstrate the performance of our approach on multiple real-world connectomics datasets with an average variation of information improvement of \FIX{$X\times$}. 
%The paper provides insights into learning shape features for top-down graph-based neuron reconstruction.
\end{abstract}
%%%%%%%%	% BODY TEXT

>>>>

%%%%%%%%% TITLE
\title{Graph-Based Neural Reconstruction \\ from Skeletonized 3D Networks}
% Neural Reconstruction Using Skeletonized 3D Networks
% Neural Reconstruction with Top-Down Enhancements from Skeletonized 3D Networks
% Graph-Based Neural Reconstruction from Morphological Skeletons
%Robust Agglomeration using 3D Skeletonization of Labeled for Connectomics}

@@

%%%%%%%%% ABSTRACT
\begin{abstract}
Advancements in electron microscopy image acquisition have created massive connectomics datasets in the terabyte range that make manual reconstruction of neuronal structures infeasible.
Current state-of-the-art automatic methods segment neural membranes at the pixel level followed by agglomeration methods to create full neuron reconstructions.
However, these approaches widely neglect global geometric properties that are inherent in the graph structure of neural wiring diagrams.
In this work, we follow bottom-up pixel-based reconstruction by a top-down graph-based method to more accurately approximate neural pathways.
We first generate skeletons in 3D from the membrane labels of the pixel-based segmentation.
We then simplify this skeletonized 3D network into a 3D graph with nodes corresponding to labels from the segmentation and edges identifying potential locations of segmentation errors.
We use a CNN classifier trained on ground truth data to generate edge weights on the 3D graph corresponding to error probabilities.
We then apply a multicut algorithm to generate a partition on the graph that improves the final segmentation.
Because the 3D graph is small and encodes top-down information our method is efficient and globally improves the neural reconstruction.
We demonstrate the performance of our approach on multiple real-world connectomics datasets with an average variation of information improvement of \FIX{$X\times$}.
%The paper provides insights into learning shape features for top-down graph-based neuron reconstruction.
\end{abstract}
%%%%%%%%	% BODY TEXT
